A theoretical analysis of the Keep Network random beacon using agent based modeling \\ \thanks{Identify applicable funding agency here. If none, delete this.}

### 2019-11-05 Mesa Simulations/Conference-LaTeX-template_7-9-18 2/paper.tex
added hypergeometric figure and edited compr expl

\subsection{Group Selection}
We model group selection using a hypergeometric distribution. For our purposes, we assume the n draws to 
be the equivalent of selecting a group of n members, with k members being malicious. We draw the sample from
a population of N virtual stakers, with K stakers being malicious.

@@

Show analytical results in comparison with simulation?

\subsection{Compromised Groups}
We use the survival function of the hypergeometric distribution to determine
the likelihood of a group of n members being compromised. To do this we evaluate
the function at the max malicious threshold.

>>>>

\subsection{Group Selection}
We model group selection using a hypergeometric distribution. For our purposes, we assume the n draws to 
be the equivalent of selecting a group of n members, with k members being malicious. We draw the sample from
a population of N virtual stakers, with K stakers being malicious. For example, 
\ref{fig: hypergeometric_distribution} shows a distribution for a group of 100 stakers. 
Based on this distribution we would expect that the number of malicous stakers in this group
would be between approx 20-40 stakers.

@@

\begin{figure}[h!]
    \includegraphics[width=\linewidth]{hypergeometric.png}
    \caption{Linear Stage Distribution}
    \label{fig: hypergeometric_distribution}
\end{figure}

\subsection{Compromised Groups}
We use the survival function of the hypergeometric distribution to determine
the likelihood of a group of n members being compromised. To do this we evaluate
the function at the max malicious threshold. Using our example above, we would
expect the percentage of compromised groups to be approximateley 50 percent
for a threshold of 25 percent.
